INTELLIGENT SYSTEMS

### 2021-03-27 paper_2.tex
fix 2.3.2

\subsection{COMPARATIVE EXPERIMENTS}
In order to evaluate the quantitative goodness of the proposed algorithm, 
three comparison metrics are used: under segmentation error (\emph{UE}) \cite{0781426514}, boundary 
recall (\emph{BR}) and achievable segmentation accuracy (\emph{ASA}) \cite{0781426508}. The 
goal is to have a low UE value, while it is preferable to have high values in BR 
and ASA. A low percentage of UE indicates that the detected boundary is made 
up of a small amount of pixels not belonging to the object to be delimited. 
A segmentation is correct when at least two boundary pixel fall from at least 
one superpixel boundary point. A high BR index indicates that the better 
segmentation is obtained. On the other hand, the ASA metric indicates the 
level of accurancy achieved in the segmentation pashe of contour, obtained 
thanks to the various labels (ground-truth) placed on each superpixel. A 
high ASA value indicates that superpixel adapt well to objects. The experiments 
were conducted on a set of 300 images belonging to the Barkeley 
Segmentation Database \cite{0781426515}.

@@

\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{*{9}{|c}|}%%{|c|c|c|c|c|c|c|c|c|}
        \hline
        & EneOpt0 & SEEDS & ERS & Lattices & NCuts & SLIC & Turbo & LSC \\
        \hline
        \bfseries{ADERENCE TO BOUNDARY} & & & & & & & & \\
        \emph{Under segmentation error} & 0.230 & 0.197 & 0.198 & 0.303 & 0.220 & 0.213 & 0.277 & \bfseries{0.190}\\
        \emph{Boundary recall} & 0.765 & 0.918 & 0.920 & 0.811 & 0.789 & 0.837 & 0.739 & \bfseries{0.926}\\
        \emph{Achievable segmentation accuracy} & 0.950 & 0.960 & 0.959 & 0.933 & 0.956 & 0.956 & 0.943 & \bfseries{0.962}\\
        \hline
        \bfseries{SEGMENTATION SPEED} & & & & & & & & \\
        \emph{Computational complexity} & $ O(N^3/K^2) $ & $ O(N) $ & $ O(N^2 \lg{N}) $ & $ O(N^{\frac{3}{2}} \lg{N}) $ & $ O(N^{\frac{3}{2}}) $ & $ O(N) $ & $ O(N) $ & $ O(N) $\\
        \emph{Average time per image} & 3.35s & \bfseries{0.0935}s & 0.969s & 0.284s & 93.4s & 0.125s & 6.61s & 0.334s\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Performance metrics superpixel segmentation algorithms at K=400}
    \label{table superpixels}
\end{table}
As we can see from the results, the worst algorithm, in terms of time, 
is \emph{NCuts}, while a good algorithm, which ranks second before \emph{LSC}, is \emph{SLIC}. 
Unlike the algorithm studied, SLIC uses an iterative K-means clustering 
performed inside different feature spaces, based only on local characteristics. 
On the other hand, LSC is able to use local and global features thanks to the 
$ \phi $  mapping function, all to have a better segmentation. Looking at the data 
in the table, this makes us understand how LSC is able to have a better BR 
value despite having a higher CP value than the previous algorithms, this 
represents the strength of this algorithm.

>>>>

\subsection{COMPARATIVE EXPERIMENTS}
In order to evaluate the quantitative goodness of the proposed algorithm, 
three comparison metrics are used: under segmentation error (\emph{UE}) \cite{0781426514}, boundary 
recall (\emph{BR}) and achievable segmentation accuracy (\emph{ASA}). The 
goal is to have a low UE value, while it is preferable to have high values in BR 
and ASA. A low percentage of UE indicates that the detected boundary is made 
up of a small amount of pixels not belonging to the object to be delimited. 
A segmentation is correct when at least two boundary pixel fall from at least 
one superpixel boundary point. A high BR index indicates that the better 
segmentation is obtained. On the other hand, the ASA metric indicates the 
level of accurancy achieved in the segmentation pashe of contour, obtained 
thanks to the various labels (ground-truth) placed on each superpixel. A 
high ASA value indicates that superpixel adapt well to objects. The experiments 
were conducted on a set of 300 images belonging to the Barkeley 
Segmentation Database \cite{0781426515}.

@@

\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{*{9}{|c}|}%%{|c|c|c|c|c|c|c|c|c|}
        \hline
        & EneOpt0 & SEEDS & ERS & Lattices & NCuts & SLIC & Turbo & LSC \\
        \hline
        \bfseries{ADERENCE TO BOUNDARY} & & & & & & & & \\
        \emph{Under segmentation error} & 0.230 & 0.197 & 0.198 & 0.303 & 0.220 & 0.213 & 0.277 & \bfseries{0.190}\\
        \emph{Boundary recall} & 0.765 & 0.918 & 0.920 & 0.811 & 0.789 & 0.837 & 0.739 & \bfseries{0.926}\\
        \emph{Achievable segmentation accuracy} & 0.950 & 0.960 & 0.959 & 0.933 & 0.956 & 0.956 & 0.943 & \bfseries{0.962}\\
        \hline
        \bfseries{SEGMENTATION SPEED} & & & & & & & & \\
        \emph{Computational complexity} & $ O(N^3/K^2) $ & $ O(N) $ & $ O(N^2 \lg{N}) $ & $ O(N^{\frac{3}{2}} \lg{N}) $ & $ O(N^{\frac{3}{2}}) $ & $ O(N) $ & $ O(N) $ & $ O(N) $\\
        \emph{Average time per image} & 3.35s & \bfseries{0.0935}s & 0.969s & 0.284s & 93.4s & 0.125s & 6.61s & 0.334s\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Performance metrics superpixel segmentation algorithms at K=400}
    \label{table superpixels}
\end{table}
As we can see from the results, the worst algorithm, in terms of time, 
is \emph{NCuts}, while a good algorithm, which ranks second before \emph{LSC}, is \emph{SLIC}. 
Unlike the algorithm studied, SLIC uses an iterative K-means clustering 
performed inside different feature spaces, based only on local characteristics. 
On the other hand, LSC is able to use local and global features thanks to the 
$ \phi $  mapping function, all to have a better segmentation. However, when 
K = 400, the CP value of the \emph{ERS} \cite{0781426508} and \emph{SEEDS} \cite{0781426509} algorithms are 0.151 
and 0.280 respectively, while the CP value of LSC is 0.366. Looking at the data 
in the table, this makes us understand how LSC is able to have a better BR 
value despite having a higher CP value than the previous algorithms, this 
represents the strength of this algorithm.

\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper2/superpixelsComparison.png}
    \centering
    \caption{Superpixel results from different algorithms. (a) SEEDS. (b) NCuts. (c) SLIC. (d) ERS. (e) LSC.}
    \label{fig: superpixelsComparison}
\end{figure}
